Bioverse: Origins of Life

### 2023-09-09 src/tex/ms.tex
formulate hypothesis H3

@@

\subsection{H3: Life only originates on planets with particular UV irradiance}
We test a UV irradiance requirement by relating the occurrence of life on a planet with a minimum past UV flux, which is a function of ...? \todo[inline]{SUKRIT}

@@

\subsubsection{Stellar flares}
Our assumptions on past UV flux neglect the contribution of stellar flares, which may be hypothesized as an alternative source of UV light~\citep{Ranjan2017}.
This concerns mainly ultracool dwarfs, due to their low quiescent emission and high pre-main sequence stellar activity~\citep{Buccino2007,West2008}.
Recent work indicates that the majority of stars show inadequate activity levels for a sufficient contribution through flares~\citep{Glazier2020,Ducrot2020,Günther2020}.
The biosignature surveys we simulated here may test the hypothesis of sufficient UV radiation via stellar flares.

>>>>

\subsection{Fraction of inhabited planets with detectable biosignatures}
Presumably, not all habitable worlds are inhabited and not all inhabited worlds develop detectable biosignatures.
The fraction of exo-Earth candidates that are both inhabited and harbor detectable biomarkers at the time when we observe them remains speculative; we aggregate them in the unitless parameter $f_\mathrm{life}$.

@@

\subsection{H3: Life only originates on planets with particular UV irradiance}
Our third theoretical experiment is to test the UV irradiance requirement (Sect.~\ref{sec:predictions:uv}) by relating the occurrence of life on a planet with a minimum past UV flux.
Here, we focus on the prebiotically interesting \SIrange{200}{280}{\nano\meter} range CITE and the quiescent stellar flux.  %~\citep{RanjanSasselov2016}.
Our concrete hypothesis shall be that life only occurs on planets that at some point in their history have received UV radiation in this wavelength range that exceeded a minimum NUV flux $F_\mathrm{NUV, min}$.
We further require this flux to have lasted for $\geq \SI{100}{\mega\year}$ to allow for a sufficient ``origins timescale''~\citep{Rimmer2023}.
We then have
\begin{equation}\label{eq:hypothesis-uv}
    H_{3} = f_\mathrm{life} (\theta, F_\mathrm{NUV}) =
        \begin{cases}
            0 , & F_\mathrm{NUV} < F_\mathrm{NUV, min}\\
            f_\mathrm{life}, & F_\mathrm{NUV} \geq F_\mathrm{NUV, min} \, \mathrm{for} \, \Delta t \geq \SI{100}{\mega\year}
        \end{cases}
\end{equation}
and the corresponding null hypothesis
%\begin{equation}
$H_{3, null} = f_\mathrm{life} (\theta),$
%\end{equation}
i.e., no correlation with UV flux.

\subsubsection{past UV flux}
\todo[inline]{\citet{Günther2020} relate U-band energy to bolometric flux.}

@@

\subsubsection{Stellar flares}
Our assumptions on past UV flux neglect the contribution of stellar flares, which may be hypothesized as an alternative source of UV light~\citep{Ranjan2017}.
This concerns mainly ultracool dwarfs, due to their low quiescent emission and high pre-main sequence stellar activity~\citep{Buccino2007,West2008}.
Recent work indicates that the majority of stars show inadequate activity levels for a sufficient contribution through flares~\citep{Glazier2020,Ducrot2020,Guenther2020}.
The biosignature surveys we simulated here may test the hypothesis of sufficient UV radiation via stellar flares.
